A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-04-16 paper.tex
Fix label conflict
Add blurb about coupling
Need to add the actual figures.  Will do when I have subfig "figured" out...

In this system, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v)$.  In our analog implementation, we use a piecewise linear approximation to the cubic, in order to simplify the circuit and avoid using expensive components.

Xu et al. used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline). Both the Morris-Lecar model and the Fitzhugh-Nagumo model have similar activator nullclines.

@@

\begin{figure}[h!]
    \label{fig: fhn_dynamics}
    \centering
    \inputtikz{figures/fhn_dynamics/fhn_dynamics}
    % TODO describe this more.
    % Show a sample trajectory in each of these.
    % remove the ticklabels
    % condense into single figure
    % Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$.
    \caption{The nullclines of the FitzHugh-Nagumo neuron.  Nullclines are isoclines where the derivative of a variable is zero.  Here we show an oscillatory mode and an excitable one.  In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.  See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
\end{figure} % TODO: legend

@@

The simulation was performed in Python, using the standard SciPy ODE solvers. % TODO list solver here

@@

\begin{figure}[h!]
    \centering
    \inputtikz{figures/neuron_unit/neuron_unit}
    \caption{The circuit we created, based of \citet{keener1983}.  Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit looks more complex, in practice it is quite simple to implement.}
    \label{fig: nagumo_ckt}
\end{figure}

- Nagumo circuit, disadvantages

- Keener improved, op amps, why is that good - scalability, etc. Piecewise (N-shaped) linear approximation.

- Our modifications - diffusion, coupling mechanism.  Some mention of mathematics involved

- Figures: circuits, circuit nullclines,

\citet{nagumo1962} proposed a circuit which could simulate the system which FitzHugh proposed.  A depiction is included in \Fref{fig: nagumo_ckt}.

>>>>

In this system, $f(v)$ can be any function which retains the appropriate dynamics, in that it has the same general shape as the cubic $f(v)$.  In our analog implementation, we use a piecewise linear approximation to the cubic, in order to simplify the circuit and avoid using expensive components.  Here, the position of the $w$-nullcline is controlled by $a$, and the vertical translation of the $v$-nullcline is controlled by $I_{ext}$

Xu et al. used a simplified two-variable model consisting of a fast, cubic-like activator variable (see the V-nullcline) and a slow, non-linear inhibitor variable (see the n-nullcline). BothThe Fitzhugh-Nagumo model has similar activator nullclines.

@@

\begin{figure}[h!]
    \label{fig: fhn_dynamics}
    \centering
    \inputtikz{figures/fhn_dynamics/fhn_dynamics}
    % TODO describe this more.
    % Show a sample trajectory in each of these.
    % remove the ticklabels
    % condense into single figure
    % .
    \caption{The nullclines of the FitzHugh-Nagumo neuron.  Nullclines are isoclines where the derivative of a variable is zero.  Here we show an oscillatory mode and an excitable one.  In an oscillating cell, the stable equilibrium is replaced by an unstable equilibrium (open circle) around which it circles indefinitely.  See \citet{parsons2018} for a clear explanation of the dynamics of oscillatory biological systems.}
\end{figure} % TODO: legend

@@

The simulation was performed in Python, using the standard SciPy ODE solvers, which wrap LSODA. % TODO list solver here

@@

\begin{figure}[h!]
    \centering
    \inputtikz{figures/neuron_unit/neuron_unit}
    \caption{The circuit we created, based of \citet{keener1983}.  Note the use of operational amplifiers in place of the inductor and tunnel diode; though this circuit looks more complex, in practice it is quite simple to implement.}
    \label{fig: neuron_unit}
\end{figure}

However, this is only one neuron.  In order to implement a full central pattern generator, we implemented diffusive coupling mechanisms.  These mechanisms are shown in \Fref{fig: coupling_ckt}.  We implemented a positive diffusion coefficient by passing the voltage through a resistor (to simulate $D$), and then a diode (to simulate $\mathrm{max}(\Delta v, 0)$).  The negative diffusion coefficient was implemented by using an inverting amplifier with a small gain, and then passing through a diode.

\subsection{Comparison of analog and simulation}
